Results

### 2018-11-20 Manuscript_draft/Results.Rmd
small changes

@@

@@

Although is not very elegant, I  had the curiosity of how a regression line will fit these 3 different families. Here I show how they fit the colud of points per family *lm(HpEffect~its_distance)*. Anyway, don't think this is very informative.

@@

Here I perform Mantel test and Procustes test between the traits and heterospecific pollen effect. For both Mantel and procustes we weren't able to find evidence of correlation between matrices. At the moment we are using all the traits without filtering the correlated traits. With Bioenv we can now what are the traits that gives a best fit of correlation between matrices. The best model is with pollen ovule ratio, stigma width and style width.

>>>>

So the higher the values HpEffect the higher the negative impact of heterospecific pollen.

@@

In total we performed 4400 treatments. If we just consider seed set, 2200 treatments including [50% Hp, 100% Hp, hand cross pollination, self pollination, natural selfing (bagged flowers) and apomixis (emasculated flowers)].

@@

Although is not very elegant, I  had the curiosity of how a regression line will fit these 3 different families. Here I show how they fit the cloud of points per family *lm(HpEffect~its_distance)*. Anyway, don't think this is very informative.

@@

Here I perform Mantel test and Procustes test between the traits and heterospecific pollen effect. For both Mantel and procustes we weren't able to find evidence of correlation between matrices. At the moment we are using all the traits without filtering the correlated traits. With Bioenv we can know what are the traits that gives a best fit of correlation between matrices. The best model is with pollen ovule ratio, stigma width and style width.
